A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-28 paper/paper.Rnw
Add abstract

\begin{abstract}
This template helps you to create a properly formatted \LaTeX\ manuscript.
\end{abstract}

>>>>

\begin{abstract}
\mt{Current practices to assess similarity in forensic shoeprint analysis typically require examiners to manually identify and label features in images of a shoe prints or outsoles. This research aims to automate such feature identification and labeling within a feature set similar to that already used by forensic examiners. A set of geometric features was developed based on common geometric shapes, such as circles and quadrilaterals. A new classifier was then trained for the pretrained convolutional neural network base of VGG16 to create a model to automatically classify portions of outsole images into the new geometric scheme of outsole class characteristics. In general, the model performs well on images with unambiguous shapes and moderate color contrast. Although systematic misclassifications arise from the inherent overlap of features in geometric shapes, model diagnostics show that such misclassifications are generally consistent and based on appropriate features
%, indicating that additional label modifications may remedy these confusions
%, indicating reasonable model performance
. Additional improvements may be realized by modifying the labeling scheme to reduce feature overlap and by preprocessing the images to improve contrast. This new approach represents a significant improvement to the current manual classification of footwear tread patterns, facilitating new modes of data collection and automatic processing that will expand the data available for assessment of footwear class characteristic frequency in the population.}
\end{abstract}
